\documentclass[fontsize=12pt]{article}

\usepackage{csvsimple}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{geometry}

\usepackage{setspace}
\doublespacing

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Markus Amano CV}
    }

\geometry{
  left=15mm,
  right=15mm,
  top=15mm,
  bottom=15mm,
}

\begin{document}

\begin{center}
  \begin{tabularx}{\textwidth} { 
      >{\raggedright\arraybackslash}X 
    >{\raggedleft\arraybackslash}X  }
    \huge Markus A.G. Amano & Cover Letter\\
    \hline
    Website: \href{https://markuspad.com/}{markuspad.com}& 
    GitHub: \href{https://github.com/inokawazu}{inokawazu}\\
    Email: markus.a.amano[at]gmail.com & \href{https://inspirehep.net/authors/1778034}{iNSPIREHEP}\\
  \end{tabularx}
\end{center}

\today

Dear PayPay Hiring Officer,

% Why am I applying
My name is Markus Amano and I am in the job market for a data centric technology job.
% how did I find this job
Looking around the internet, I found this particular job via the privately owned
dev blog, \url{tokyodev.com}.
% what are some relavant skills I have.
I believe I am well equipped with with experiences, skill, and education to satisfactorily 
carry out the duties required of me of this job at PayPay.

% Explain why I am  interested in this particular work.
I fundamentally enjoy tackling difficult technical problems.
%
Such problems usually manifest themselves as math and physics problems, but both such 
fields commonly share one aspect - data.
%
For PayPay to handle the vast amounts of data from the increasing larger amount of 
transactions in 2023, the underlying systems must be well oiled such that the tight loops of 
repeated model evaluation and code must be lighting fast.
%
I enjoy and look forward to possibly being able to tackle such intriguing problems of scale, 
where every percent of improvement is profoundly important. 
% What are some points on my resume that might be relavant here?
% What are some relavant work experiences I have had.
% How do I satisfactorily, meet the job requirements.
%
% Bachelors in a quantitative field such as Computer Science, Mathematics, Statistics, Machine Learning, or equivalent
I have Bachelors of Science in Engineering Physics from the Colorado School of Mines and a PhD in theoretical physics from The University of Alabama.
% Excellent verbal and written communication skills in English and/or Japanese
Being born and raised in the USA I am fluent in English.
Practicing since 2014, I have attained a conversational ability in Japanese. 
%
I continue to practice my Japanese to this day and look forward to chance use such a 
linguistic skill.
% More than three years of experience as a data scientist, machine learning engineer, or equivalent role
As my current main job, I do post-doctoral research here are the Henan University 
in Kaifeng, China.
%
On the side, I have been doing freelance work (similar work here) for about two years.
%
The amount of freelance jobs is possible too varied to list out here, but I will endeavor to 
provided freelance jobs of note.
%
I have created interactive visualization tools that can be used to explore health data of 
the European Union.
%
I have created a Naive Bayes model to classify patients depending on written symptoms.
%
I also have done and am currently doing contractor work for \textit{Quantum Data Center} to help them develop Mixed Integer Programs that optimize plane traffic.
%
From these professional experiences I have had the fortune be familiar and become more 
proficient with development, maintenance, testing, customer relations, etc.
% Experience in at least one primary language (e.g., Java, Scala, Python) and SQL (any variant) 
I enjoy learning new languages but I would admit that I have three primary languages: 
\textbf{Julia} (4 years), \textbf{Python} (7 years), and \textbf{Mathematica} (6 years).
%
I also have some experience with using with \textbf{SQL} databases.
% Experience in one or more machine learning frameworks such as TensorFlow, PyTorch, Theano, etc.
I am familiar with TensorFlow and the construction of such models.

Thanks for you consideration of my application.
%
I am willing to start as soon as and would be willing to be flexible to do a online 
interview at the request of the interviewer.
%
I am reachable at this email \textit{markus.a.amano[at]gmail.com} 
and my number is \textit{+86 166 1388 9791}.

Sincerely,

Markus Amano
\end{document}
